Enter our title here

### 2017-08-13 manuscript.tex
added competing technologies

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to 
unfold, the use of statistical software has become increasingly emphasized in statistics education. By integrating the 
capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and 
interpreting real data sets (Chance2007), giving them an authentic view of how statistics is practiced outside of the 
classroom (Broaddus2013). The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} (GAISE) 
College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).

The goal for any introductory statistics course is to help students develope the ability to think statistically (AmericanStatisticalAssociation2016). 
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as variability, randomness and simulation.

Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses (Chance2007). R allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark an interest in the domain of statistics.

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R.

For a statistical learning tool to be effective, the software system should be modular, extensible, reproducable, and web-based (Hare2017).

>>>>

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to 
unfold, the use of statistical software has become increasingly emphasized in statistics education. By integrating the 
capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and 
interpreting real data sets \citep{Chance2007}, giving them an authentic view of how statistics is practiced outside of the 
classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} 
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators 
to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).

The goal for any introductory statistics course is to help students develope the ability to think statistically 
\citep{AmericanStatisticalAssociation2016}. 
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and simulation.

Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} provide extensive statistical capabilites 
(free of charge) and are commonly used in statistics courses \citep{Chance2007}. R allows students to explore real-world data 
sets which can not only enhance their understanding of concepts, but can also spark an interest in the domain of statistics 
\citep{Wang2017}.

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
popular interactive teaching technologies have been created including Swirl (need to cite this), LearnR and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback. Swirl is an open source R software package 
that users access in their R console. This interactive learning tool contains several pre-existing lessons but what makes 
Swirl so popular is its versitality; educators can create their own lesson (or tailor a pre-existing one) to fit their 
curriculum and assign it to students. TryR (Code School 2014) and LearnR are web-based programs and do not have this 
reproducible capability. Public content authoring is not available so educators are limited on what they can teach their 
students. The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is 
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with 
software than the statistical concepts themselves \citep{Hare2017}.

A not so popular interactive teaching tool is DataCamp- a web application where students can take existing courses or lessons 
that their instructure created.

For a statistical learning tool to be effective, the software system should be modular, extensible, reproducable, and web-
based (Hare2017).
